
\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

% Custom formatting
\pagestyle{empty}
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=1.2em}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdftitle={MD. Fahad Ali - CV},
    pdfauthor={MD. Fahad Ali}
}

% Section formatting
\titleformat{\section}{
  \large\bfseries\uppercase
}{}{0em}{}[\titlerule]

% Custom command for experience entries
\newcommand{\expentry}[3]{%
  \vspace{4pt}%
  \noindent\textbf{#1} - #2 \hfill \textbf{#3}\\[-2pt]%
}

\begin{document}

% Header Section
\begin{center}
  {\huge\textbf{MD. Fahad Ali}}\\[0.3cm]
  Full Stack Developer\\[0.4cm]
  {\footnotesize fahad288ali@gmail.com \textbar{} +8801867758990 \textbar{} }
\end{center}

\vspace{0.2cm}

% Summary Section
\section{Professional Summary}
\noindent Full Stack Developer specializing in the JavaScript/TypeScript ecosystem, particularly Next.js, Node.js, Fastify, and Express.js. Experienced in architecting and deploying scalable SaaS applications, as well as building AI-powered platforms integrated with RAG pipelines, PostgreSQL, and PGVector. Strong background in designing robust backend systems, automating CRM and presentation workflows, and developing interactive, canvas-based frontend visualizations. Focused on delivering reliable, containerized solutions using Docker that efficiently handle high concurrent user traffic.


\vspace{0.2cm}

% Experience Section
\section{Experience}
\expentry{SolveTech Solution}{Full Stack Developer}{Sep 2025 - Present}
\begin{itemize}
  \item Developed PropDNA.ai, an AI-powered real estate analytics platform using Next.js, Fastify, RAG, PostgreSQL, Docker, and Konva for interactive canvas-based visualizations.
  \item Architected an AI-powered slide generation system that automates presentation creation, utilizing advanced LLMs for intelligent content generation and seamless layout optimization.
  \item Implemented Go High Level customizations for CRM workflows, enhancing automation and client management capabilities for marketing agencies.
  \item Integrated RAG pipelines with PostgreSQL and PGVector for advanced semantic search and AI-driven content retrieval.
\end{itemize}

\expentry{NASA Space Apps Challenge Hackathon}{Member}{Sep 2024 - Sep 2024}
\begin{itemize}
  \item Built a prototype named 'Existence', an educational tool on solar flares and the solar system, enhancing understanding of space phenomena.
  \item Advanced to the preliminary round of the NASA Space Apps Challenge among 100+ teams.
\end{itemize}

\expentry{Pirhotech.com}{Full Stack Developer}{Jul 2023 - Sep 2025}
\begin{itemize}
  \item Developed and deployed multiple SaaS and e-commerce applications, scaling to handle 700+ concurrent users.
  \item Built secure, high-performance systems with Next.js, Node.js, PostgreSQL, and Docker, ensuring reliability and scalability.
  \item Collaborated with organisations like Biddarthi to design and deliver scalable, production-ready platforms.
\end{itemize}

\expentry{Devsonket}{Open Source Contributor}{Mar 2023 - May 2023}
\begin{itemize}
  \item Improved developer documentation at Devsonket, increasing clarity for 500+ monthly users (JavaScript, Python).
  \item Maintained Puppeteer.js Cheat Sheets, helping 300+ developers with browser automation.
\end{itemize}


% Education Section
\section{Education}
\textbf{B.Sc. (Hons) in Computer Science \& Engineering} - Green University of Bangladesh \hfill \textbf{2026}\\[2pt]
\textbf{Higher Secondary Certificate} - Cantonment Public School \& College \hfill \textbf{2021}\\[2pt]
\textbf{Secondary School Certificate} - Cantonment Public School \& College \hfill \textbf{2018}\\[2pt]


% Projects Section
\section{Projects}
\textbf{AI-based Educational Platform with Gamification}\\
An AI-powered learning platform featuring a real-time chatbot and gamified badge system with real-time WebSocket architecture allowing multiple students to seamlessly participate in live, AI-generated challenges.\\
\textbf{Tech Stack:} Next.js, Node.js, Socket.IO, Render
\vspace{4pt}
\textbf{Turfslot.com — Booking platform for turf}\\
A robust turf booking platform handling 100+ daily transactions with seamless payment integration.\\
\textbf{Tech Stack:} Next.js, Express.js, Supabase, SSLCommerz
\vspace{4pt}
\textbf{Biddarthi.org — A platform for selling courses}\\
A comprehensive course-selling platform serving 700+ active students with integrated secure payment gateways.\\
\textbf{Tech Stack:} Next.js, PostgreSQL, SSLCommerz, LaTeX
\vspace{4pt}
\textbf{Real-Time Chat App}\\
A real-time chat application featuring instant messaging, typing indicators, and reliable online status tracking.\\
\textbf{Tech Stack:} Next.js, Express.js, Socket.IO
\vspace{4pt}


% Skills Section
\section{Skills}
\textbf{AI \& LLM Tools}: LangChain, RAG (Retrieval-Augmented Generation), PGVector\\
\textbf{Backend Development}: Node.js, Express.js, Fastify, REST API, GraphQL, Socket.IO\\
\textbf{Databases}: PostgreSQL, MongoDB, SQL\\
\textbf{DevOps \& Cloud}: Docker, AWS, Vercel\\
\textbf{Frontend Development}: JavaScript, TypeScript, React, Next.js, TailwindCSS, WebGL, Three.js\\
\textbf{Tools \& Utilities}: Git, GitHub, Bash\\
\textbf{Languages}: English (Fluent), Bangla (Native)

% Certifications Section (if exists)
\section{Certificate}


\end{document}
